Reproducibility in plant pathology: where do we stand and a way forward

### 2022-04-30 analysis/paper/paper.Rmd
replace "often" with frequently
Remove the word "often"

MEGA was the most widely cited software in this evaluation reflecting the wide spread use of sequence analysis in the field of plant pathology.
The second, third and fourth, and eighth most often cited software packages were all statistical programs.
SAS remains firmly entrenched in the discipline as the choice of software for statistical analysis followed by SPSS but R is not far removed from SPSS in fourth place with Statistica and Genstat tied for eighth.
The remainder of the top ten software packages we found were related to sequence analysis, *i.e.*, BLAST, Clustal and BioEdit, phylogenetic analysis MrBayes or the general-purpose spreadsheet program Excel&reg;.
It is interesting to note however, that with the popularity of Python that it only appears in the survey twice and in 2020 in both articles, not enough times to be in the top 10 most-cited.

@@

We believe that adopting an attitude of open and collaborative science and using the best reproducibility practices in our daily work, directly benefits us as researchers.
For example, between complicated analyses, reviews and revisions and questions years later about the data that was collected or analysis that was conducted, it is extremely beneficial to be able to easily reproduce your work quickly and easily.
This letter was drafted over the course of several years as the authors had time to devote to it.
Having everything in a reproducible framework made it easy to resume work and set-aside as necessary without losing information and having everything well-documented made it more simple to do this.
Second, it benefits the reviewer by aiding their understanding of the work done and gives them more materials to use to make suggestions for improvements when reviewing and the end-user or reader is better able to verify the validity of the methods used and recreate the analysis.
Perhaps more importantly, sharing these details help with knowledge transfer by showing other interested parties how something was done rather than simply describing it.
Lastly, openly sharing your work and making it discoverable can lead to new collaborations and synergistic ideas.
One of the most important messages that we would like to share is that there is more to the work than just the paper.
Sharing materials detailing the analysis that was performed and documenting the data provide citable products and enhance the manuscript providing the reader with a richer set of information with which to understand the work that was performed.
This open sharing of code and data often leads to greater impact as work is cited if resources such as code or data are reused.
With mandates for openly sharing data becoming more common with funding agencies, we can and should embrace this and move the discipline forward and have a greater impact with our work.

>>>>

MEGA was the most widely cited software in this evaluation reflecting the wide spread use of sequence analysis in the field of plant pathology.
The second, third and fourth, and eighth most frequently cited software packages were all statistical programs.
SAS remains firmly entrenched in the discipline as the choice of software for statistical analysis followed by SPSS but R is not far removed from SPSS in fourth place with Statistica and Genstat tied for eighth.
The remainder of the top ten software packages we found were related to sequence analysis, *i.e.*, BLAST, Clustal and BioEdit, phylogenetic analysis MrBayes or the general-purpose spreadsheet program Excel&reg;.
It is interesting to note however, that with the popularity of Python that it only appears in the survey twice and in 2020 in both articles, not enough times to be in the top 10 most-cited.

@@

We believe that adopting an attitude of open and collaborative science and using the best reproducibility practices in our daily work, directly benefits us as researchers.
For example, between complicated analyses, reviews and revisions and questions years later about the data that was collected or analysis that was conducted, it is extremely beneficial to be able to easily reproduce your work quickly and easily.
This letter was drafted over the course of several years as the authors had time to devote to it.
Having everything in a reproducible framework made it easy to resume work and set-aside as necessary without losing information and having everything well-documented made it more simple to do this.
Second, it benefits the reviewer by aiding their understanding of the work done and gives them more materials to use to make suggestions for improvements when reviewing and the end-user or reader is better able to verify the validity of the methods used and recreate the analysis.
Perhaps more importantly, sharing these details help with knowledge transfer by showing other interested parties how something was done rather than simply describing it.
Lastly, openly sharing your work and making it discoverable can lead to new collaborations and synergistic ideas.
One of the most important messages that we would like to share is that there is more to the work than just the paper.
Sharing materials detailing the analysis that was performed and documenting the data provide citable products and enhance the manuscript providing the reader with a richer set of information with which to understand the work that was performed.
This open sharing of code and data leads to greater impact as work is cited if resources such as code or data are reused.
With mandates for openly sharing data becoming more common with funding agencies, we can and should embrace this and move the discipline forward and have a greater impact with our work.
